The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-09-22 paper/draft.tex
include refs

Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact that some lineages radiate explosively following
island colonisation, while others remain one single species (Price/Chase).

>>>>

Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact that some lineages radiate explosively following
island colonisation, while others remain one single species (Price/Chase) (eg. \cite{price2004speciationPrice}).

Also: Ecological Opportunity and Adaptive Radiation, Stroud & Losos 2016: ``Does the concept have predictive value[...]?'' \cite{stroud2016ecological}
Phylogenetic niche conservatism, phylogenetic signal and the relationship between phylogenetic relatedness and ecological similarity among species, Losos 2008: ecological vs. phylogenetic similarity \cite{losos2008phylogenetic}
